### 2019-06-17 initial/notes.tex
check in notes

Thus, in our toy model, we \emph{cannot} choose a simple form e.g.\
$\rd{\alpha}{t} = -\epsilon\alpha$, it must have differing signs over
$\mathcal{C}_i$.

>>>>

Thus, in our toy model, we \emph{cannot} choose a simple form e.g.\
$\rd{\alpha}{t} = -\epsilon\alpha$, it must have differing signs over
$\mathcal{C}_i$. Let's consider a model where $\dot{\eta} = +\epsilon \eta \mu$.
It should be noted that, upon careful calculation, $\dot{\eta} = -\epsilon \eta
\mu$ will \emph{not} result in any captures! We will see this below.

Our expression then becomes (using our usual decomposition $\mu = \bar{\mu} +
\mu'$ where $\bar{\mu} = \mu_4 \approx \cos I/\alpha$)
\begin{align*}
    B_i &= \int -\frac{\epsilon \mu}{\alpha}\frac{\mu^2}{2}\;\mathrm{d}t,\\
        &\approx \int \frac{\epsilon \mu^3}{2\alpha \mu'}.
\end{align*}
It may be tempting now to predict $B_{top} = -\frac{2\pi \epsilon 4\sin
I/\alpha}{2\alpha^2}$, by directly substituting $\mu \approx \mu'$, and use the
same $\mu^3 = \mu'\p*{2\bar{\mu}\mu'}$ trick as in toy problem 1 to get an
antisymmetric term and obtain
\begin{equation}
    B_{tot} = -\frac{4\pi \epsilon 2\sqrt{\frac{\sin I}{\alpha}}\frac{\cos
        I}{\alpha}}{2\alpha^2}.
\end{equation}
This predicts a capture probability $P_c = \frac{\cos I}{\sqrt{\sin
I}}\sqrt{\eta}$ where again $\eta\alpha = 1$. We note that this is \emph{not} in
accordance with our calculations, which predict $P_{c} \propto \eta^0$! Further
investigation necessary.
